A generalized definition of multidimensional item response theory parameters

### 2023-01-13 output/paper_draft/paper_M2PLM_parameters.Rmd
Changes knit hooks to new version compatible with Quarto

```{r setup, include=FALSE}
# Includes:

@@

```{r write-bib, cache=TRUE}
# automatically create a bib database for R packages
write_bib(
  c(.packages(), 'bookdown', 'knitr', 'rmarkdown'),
  'www/packages.bib'
)
```

```{r sources, cache=FALSE, include=FALSE}
source("R/Formulae.R", encoding = 'UTF-8')
```

@@

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$,
defined by vector space $V$ and basis $`r LS_BASIS_EQ`$.
A respondent is represented by vector $`r TRAIT_VEC_IN_LS`$,
which is assumed to be a multivariate normal random variable:

@@

According to the M2PL model, the probability of a positive response to item
$`r ITEM_INDEX`$ is

@@

where $`r DISCR_VECTOR`$ is a $`r N_DIMS`$-dimensional vector of discrimination
parameters, and $`r INTERCEPT_PARAM`$ an intercept parameter related to the
location of the item in the latent space.

@@

Our aim is to find the point of maximum slope of $`r IRF_ABBR`$ in
$`r LATENT_SPACE`$. As in @reckase_difficulty_1985, we need to
reparameterize Equation \@ref(eq:M2PL-formulation) in polar coordinates,
because the slope is dependent on the direction considered.
However, Reckase's Equation 3 implicitly assumes orthogonality.
In order to contemplate the general case,
we need to introduce a few linear algebra results before proceeding further.

## Linear algebra of non-orthogonal coordinates

Let's consider the standard basis $`r LS_STD_BASIS_EQ`$ in $`r LATENT_SPACE`$.
We can write all $`r TRAIT_VEC_IN_LS`$ as a linear combination of each baseis.
Therefore, we have both representations: $`r TRAIT_VECTOR_DEF_BASIS_EQ`$, and
$`r TRAIT_VECTOR_DEF_STD_BASIS_EQ`$, where $`r TRAIT_COORDS_EQ`$ and
$`r TRAIT_COORDS_STD_EQ`$.

Let $`r BASIS_CHANGE_DEF`$ be the change of basis matrix; then, we have that

\begin{equation}
  `r BASIS_CHANGE`.                                          (\#eq:change-basis)
\end{equation}

The $`r DIM_INDEX`$-th column of $`r TRANSFORM_MATRIX`$ is given by the
coordinates of $`r BASIS_VECTOR_ANY`$ in basis $`r LS_STD_BASIS`$.
If $`r BASIS_VECTOR_ANY_TRANSF_EQ`$, then

\begin{equation}
  `r TRANSFORM_MATRIX_EQ`.                           (\#eq:transform-matrix-def)
\end{equation}

With the standard basis in $`r LATENT_SPACE`$ we have the usual scalar product.
With basis $`r LS_BASIS`$ in $`r LATENT_SPACE`$ we define an inner product
$`r LS_BASIS_INNER_PROD`$, such that the norm of $`r TRAIT_VECTOR`$ is
invariant, i.e., $`r TRAIT_NORM_EQ`$. Therefore,

\begin{equation}
  `r TRAIT_NORM_STD_SQ_EQ`.                             (\#eq:inner-product-def)
\end{equation}

Thus, we must define the inner product $`r LS_BASIS_INNER_PROD`$ with Gram
matrix $`r INNER_PROD_MAT_EQ`$. That is, $`r INNER_PROD_EQ`$, which keeps the
norm invariant.

The Gram matrix has $`r INNER_PROD_MAT_ELEMENT_EQ`$ as element. As
$`r TRANSFORM_MATRIX`$ (and consequently $`r TRANSFORM_MATRIX_TRANSP`$) is
invertible, so $`r INNER_PROD_MATRIX`$ is, and $`r INNER_PROD_MATRIX_INV_EQ`$.

The cosines between two vectors follow the usual definition,

@@

Let's consider now the vectors $`r DIR_COS_VEC`$ and $`r DIR_COS_VEC_STD`$, made
up by the $`r N_DIMS`$ direction cosines of $`r TRAIT_VECTOR`$ with the basis
vectors of $`r LS_BASIS`$ and $`r LS_STD_BASIS`$, respectively.

::: {#prp-dir-cosines-generalized-basis}

**Proposition 1** Under the previously defined conditions, for all
$`r TRAIT_VEC_IN_LS`$,

\begin{equation}
  `r DIR_COS_VEC_EQ`                              (\#eq:direction-cosine-vector)
\end{equation}

with

\begin{equation}
  `r DIAG_MATRIX_INNER_PROD_EQ`.
\end{equation}

Therefore,

@@

::: {.proof}
*Proof.*

For every $`r DIM_INDEX`$; $`r DIM_ENUM_EQ`$,

\begin{equation}
  `r DIR_COSINE_PROOF_EQ`,
\end{equation}

with $`r INNER_PROD_MATRIX_ROW`$ the $`r DIM_INDEX`$-th row of
$`r INNER_PROD_MATRIX`$.

Therefore, $`r DIR_COS_VEC_EQ`$ and $`r TRAIT_VECTOR_POLAR_EQ`$.
$`r END_OF_PROOF`$
:::

:::

We can also obtain a result that relates the direction cosines of any two bases.

::: {#prp-dir-cosines-bases-relationship}

**Proposition 2** Let's consider another basis $`r ALT_BASIS_EQ`$ in
$`r LATENT_SPACE`$ and the inner product $`r ALT_BASIS_INNER_PROD`$ that keeps
the norm of the Euclidean space invariant.

Let $`r DIR_COS_VEC_ALT`$ be the vector of direction cosines of
$`r TRAIT_VECTOR`$ in $`r ALT_BASIS`$ (i.e., the cosines with the elements of
$`r ALT_BASIS`$).

Then,

\begin{equation}
  `r DIR_COS_VEC_ALT_EQ`,                      (\#eq:dir-cosines-transformation)
\end{equation}

where

\begin{equation}
  `r DIAG_MATRIX_INNER_PROD_ALT_EQ`
\end{equation}

and $`r TRANSFORM_MATRIX_ALT_EQ`$.

::: {.proof}
*Proof.*

Let's call $`r TRAIT_COORDS_ALT_EQ`$ and let $`r TRANSFORM_MATRIX_ALT_EQ`$
be the change of basis matrix, such that $`r TRAIT_TRANSFORM_ALT_EQ`$.

Then, we have that $`r BASIS_CHANGE_ORG_ALT_EQ`$.

The inner product $`r ALT_BASIS_INNER_PROD`$ that keeps the norm invariant is
defined by $`r INNER_PROD_TRAIT_ALT_EQ`$, and we define
$`r INNER_PROD_MATRIX_ALT_EQ`$.

By proposition 1, for each case we have:

1. $`r TRAIT_VEC_STD_POLAR_EQ`$

1. $`r TRAIT_VECTOR_POLAR_EQ`$

1. $`r TRAIT_VEC_ALT_POLAR_EQ`$

Given (1),

\begin{equation}
  `r TRAIT_VEC_STD_POLAR_EQ_XPAND`
\end{equation}

and

\begin{equation}
  `r TRAIT_VEC_ALT_POLAR_ALT_EQ`.
\end{equation}

Using (2) and (3) we get that

\begin{equation}
  `r TRAIT_VEC_STD_POLAR_ORG_EQ`
\end{equation}

and

\begin{equation}
  `r TRAIT_VEC_STD_POLAR_ALT_EQ`.
\end{equation}

Therefore,

\begin{equation}
  `r TRAIT_VEC_POLAR_ORG_ALT_COEFF_EQ`,
\end{equation}

and thus $`r DIR_COS_VEC_ALT_EQ`$.$`r END_OF_PROOF`$

:::

:::

From Proposition 1,
any trait vector $`r TRAIT_VECTOR`$ is expressed in polar coordinates as

\begin{equation}
  `r TRAIT_VECTOR_POLAR_EQ`.                      (\#eq:trait-equivalence-polar)
\end{equation}

@@

Following the procedure outlined by @reckase_difficulty_1985
[@reckase_discriminating_1991],
we first compute the point of maximum slope by finding the root(s) of
the second derivative with respect to $`r TRAIT_NORM`$.

The slope in direction $`r DIR_ANGLE_VEC`$ is given by

\begin{equation}
  `r IRF_1ST_DIFF_EQ`,                                      (\#eq:M2PL-1st-diff)
\end{equation}

and

@@

The root we are interested in is found for $`r IRF_MAX_SLOPE_EQ`$
(the other ones occur when $`r IRF_ABBR`$ equals 0 and 1,
which result in improper values of $`r TRAIT_NORM`$).

The slope in direction $`r DIR_ANGLE_VEC`$ when $`r IRF_MAX_SLOPE_EQ`$ is given
by

@@

Notation aside, these equations differ from
Reckase's [-@reckase_difficulty_1985] Equations 3 through 6
only in the term $`r INNER_PROD_INV_DIAG_SQ_PROD`$.

To compute the direction of the maximum slope,
Reckase leverages on the property that the squared direction cosines sum up to 1
(see Equation 7 therein).
However, this assertion implicitly assumes orthogonal coordinates,
so it does not apply in general to $`r DIR_COS_VEC`$.
Instead, we may consider the direction cosine vector with the standard basis
$`r LS_STD_BASIS`$.
Now, applying Proposition 2 (with $`r ALT_MATRIX_AS_ID`$) we obtain

\begin{equation}
  \begin{split}
    `r DIR_COS_AS_DIR_COS_STD_EQ` \\
    `r TRAIT_POLAR_COEFF_COS_STD_EQ`.
  \end{split}                                 (\#eq:direction-cosine-vectors-eq)
\end{equation}

Therefore, substituting in \@ref(eq:slope-max),

@@

We can then define

\begin{equation}
  `r DISCR_VECTOR_STD_EQ`                                (\#eq:discr-vector-std)
\end{equation}

so

\begin{equation}
  `r SLOPE_MAX_STD_EQ`.                                     (\#eq:slope-max-std)
\end{equation}

We are thus considering the direction cosines with respect to the orthogonal
axes, so we can just apply @reckase_difficulty_1985's results, obtaining

\begin{equation}
  `r DIR_COS_VEC_STD_EQ`.                                 (\#eq:dir-cos-vec-std)
\end{equation}

Substituting $`r DIR_COS_VEC_STD`$
(Equation \@ref(eq:direction-cosine-vectors-eq)) and
$`r DISCR_VECTOR_STD`$ (Equation \@ref(eq:discr-vector-std))
by their respective expressions results in the
expression for the direction cosine vector of item $i$ in $`r LATENT_SPACE`$,

@@

which gives the direction from the origin to the point where
the slope is maximum.
Finally, to determine the signed distance $`r DISTANCE_PARAM`$
from the origin to that point,
we solve Equation \@ref(eq:M2PL-formula-polar) for $`r IRF_MAX_SLOPE_EQ`$ to get
$`r TRAIT_NORM_SOLVED_EQ`$. Using equation \@ref(eq:dir-cos-vec), then

@@

The slope $`r SLOPE_MAX_PARAM`$ at the point defined by Equations
\@ref(eq:dir-cos-vec) and \@ref(eq:distance-param)
is given by Equation \@ref(eq:slope-max).
Substituting Equation \@ref(eq:dir-cos-vec) in Equation \@ref(eq:slope-max),
[@reckase_discriminating_1991],

@@

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
Equation \@ref(eq:slope-param) makes it clear that a space $`r TEST_SPACE`$
with basis $`r ITEM_SPACE_BASIS_EQ`$ and inner product matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined,
such that $`r INNER_PROD_DISCR_EQ`$ and, subsequently,
$`r DISCR_VECTOR_MODULE_EQ`$.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of the
discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces,
as their inner product matrices are inverse of one another.

With this definition we have that

\begin{equation}
  \begin{split}
    `r DIR_COS_ITEM_VEC_NORM_EQ` \\
    `r DISTANCE_PARAM_NORM_EQ`   \\
    `r SLOPE_MAX_PARAM_NORM_EQ`.
  \end{split}                             (\#eq:item-params-discrimination-norm)
\end{equation}

It is clear that $`r INNER_PROD_INV_MAT_ELEMENT_EQ`$ were
$`r INNER_PROD_INV_MAT_ELEMENT`$ is the $`r INNER_PROD_INV_MAT_SUBINDEX`$-th
element of $`r INNER_PROD_MATRIX_INV`$.

Let $`r LS_STD_BASIS`$ be the standard basis of $`r TEST_SPACE`$.
Then, $`r BASIS_CHANGE_TS_EQ`$ is the change of basis matrix and
$`r DISCR_VECTOR_STD_MOD_EQ`$.

Applying propositon 1,

@@

@@

```{r set-flextable-wd, cache=FALSE}
# Necessary for officedown to find the template file:
opts_knit$set(root.dir = DOC_DIR)
```

```{r example-items-table-out, cache=FALSE, tab.id="example-items-table-out", tab.cap="Item parameters for the graphical example"}
item_params_output
```

@@

```{r item-plot-out, cache=FALSE, fig.cap="Item plots in an orthogonal (left) and oblique (right) test space.", fig.height=3.1, fig.width=6.65}
plot_orth + plot_oblique
```

@@

```{r read-chunks-empirical-example}
read_chunk("src/Empirical_example_Tezza2018.R")
```

@@

```{r set-flextable-wd, cache=FALSE}
```

@@

```{r empirical-items-table-out, cache=FALSE, tab.id="empirical-items-table-out", tab.cap="Item parameters for the empirical example"}
item_params_output
```

>>>>

```{r setup}
#| include: false

# Includes:

@@

```{r write-bib}
#| cache: true

# automatically create a bib database for R packages
write_bib(
  c(.packages(), 'bookdown', 'knitr', 'rmarkdown'),
  'www/packages.bib'
)
```

```{r sources}
#| cache:   false
#| include: false
source("R/Formulae.R", encoding = 'UTF-8')
```

@@

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$,
defined by vector space $V$ and basis $`r LS_BASIS`$,
being $`r LS_BASIS_EQ`$ an arbitrary set of linearly independent vectors.
A respondent is represented by vector $`r TRAIT_VEC_IN_LS`$,
with coordinates $`r TRAIT_VECTOR`$ in $`r LATENT_SPACE`$,
which is assumed to be a multivariate normal random variable:

@@

As in @reckase_difficulty_1985, the characteristic function of item
$`r ITEM_INDEX`$ according to the M2PL model is formulated as follows:

@@

being  
$`r IRF_M2PL`$ ($= `r IRF_ABBR`$ henceforth, for simplicity) the probability of
a positive response to item $`r ITEM_INDEX`$ for a given $`r TRAIT_VECTOR`$,  
$`r DISCR_VECTOR`$ a $`r N_DIMS`$-dimensional vector of
discrimination parameters, and  
$`r INTERCEPT_PARAM`$ an intercept parameter related to the location of the item
in the latent space.

@@

Our aim is to find the point of maximum slope of $`r IRF_ABBR`$ in
$`r LATENT_SPACE`$. As in @reckase_difficulty_1985, we need to
reparameterize Equation \@ref(eq:M2PL-formulation) in polar coordinates,
because the slope is dependent on the direction considered.
However, Reckase's Equation 3 implicitly assumes orthogonality.
In order to contemplate the general case,
we need to introduce a few linear algebra results before proceeding futher.

## Linear algebra of non-orthogonal coordinates
<!-- # TODO: To appendix, OR citation about these? -->

### Inner product

Let $`r INNER_PROD_EQ`$ be the inner product in $`r LATENT_SPACE`$, with
the positive-definite matrix $`r INNER_PROD_MATRIX`$ its inner product matrix.
We may apply a change of basis in $`r LATENT_SPACE`$ that results in a space
$`r LATENT_SPACE_STD`$ with the standard basis $`r LS_STD_BASIS_EQ`$.
Such a change of basis can be defined as

\begin{equation}
  `r BASIS_CHANGE`,                                          (\#eq:change-basis)
\end{equation}

with $`r TRAIT_VECTOR_STD`$ the coordinates
of $`r TRAIT_VECTOR`$ in $`r LATENT_SPACE_STD`$ and $`r TRANSFORM_MATRIX_EQ`$
(being $`r BASIS_VECTOR_ANY_TRANSF`$ the coordinates of
$`r BASIS_VECTOR_ANY`$ in $`r LATENT_SPACE_STD`$
for any dimension $`r DIM_INDEX`$).
This new space can be defined as a Euclidean space with standard inner product
(i.e. dot product), such that the norm $`r NORM_EQ`$ of $`r TRAIT_VECTOR`$
in $`r LATENT_SPACE_STD`$ is given by<!-- # TODO: Reference needed? -->

\begin{equation}
  `r TRAIT_MODULE`^2 = `r TRAIT_VECTOR_STD_SQ` =
    `r TRANSF_TRAIT_SQUARED` =
    `r TRAIT_TRANSF_TRAIT`.                                 (\#eq:inner-product)
\end{equation}

Thus, the inner product matrix $`r INNER_PROD_MATRIX`$ in $`r LATENT_SPACE`$
is consistently defined as

\begin{equation}
  `r INNER_PROD_MAT_EQ`.                            (\#eq:inner-prod-matrix-def)
\end{equation}

### Direction cosines

The cosines between two vectors follow the usual definition,
<!-- # TODO: Is this true?? See Harman 1970 (eq. 4.43, p. 60 to check) -->

@@

By Equation \@ref(eq:inner-prod-matrix-def) it is clear that
$`r DIAG_INNER_PROD_MATRIX_EQ`$
(but note that the basis vectors are not necessarily unitary).
By defining $`r DIAG_MATRIX_INNER_PROD`$ as
the diagonal matrix with the same diagonal as $`r INNER_PROD_MATRIX`$,
Equation \@ref(eq:direction-cosine) in matrix notation is<!-- # TODO:
Not sure if it’s necessary to explain this further.
There may be a certain “inferential leap” assuming that D^(-1/2) is
the matrix form equivalent to 1/u_k,
(but I “know” intuitively that the generalization holds) -->

\begin{equation}
  `r DIR_COS_VEC_EQ`.                             (\#eq:direction-cosine-vector)
\end{equation}

From Equation \@ref(eq:direction-cosine-vector),
any trait vector $`r TRAIT_VECTOR`$ is expressed in polar coordinates as

@@

@@

Following the procedure outlined by @reckase_difficulty_1985
[@reckase_discriminating_1991],
we first compute the point of maximum slope by finding the root(s) of
the second derivative with respect to $`r TRAIT_MODULE`$.

@@

The root we are interested in is found for $`r IRF_MAX_SLOPE_EQ`$
(the other ones occur when $`r IRF_ABBR`$ equals 0 and 1,
which result in improper values of $`r TRAIT_MODULE`$).
The slope in direction $`r DIR_ANGLE_VEC`$ is given by

\begin{equation}
  `r IRF_1ST_DIFF_EQ`.                                      (\#eq:M2PL-1st-diff)
\end{equation}

When $`r IRF_MAX_SLOPE_EQ`$,

@@

Notation aside, these equations differ from
Reckase's [-@reckase_difficulty_1985] Equations 3 through 6
only in the term $`r INNER_PROD_INV_DIAG_SQ_PROD`$.
When $`r LS_BASIS`$ is the standard basis,
this term simplifies to an identity matrix
(which results in Equation \@ref(eq:M2PL-formula-polar) through
\@ref(eq:slope-max) simplyfing to rectangular Cartesian coordinates,
i.e. the equations outlined by Reckase).
To compute the direction of the maximum slope,
Reckase leverages on the property that the squared direction cosines sum up to 1
(see Equation 7 therein).
However, this assertion implicitly assumes orthogonal coordinates,
so it does not apply in general to $`r DIR_COS_VEC`$.<!-- # TODO: To appendix the following, or maybe give for granted? -->
Instead, we may consider the direction cosine vector in $`r LATENT_SPACE_STD`$:

\begin{equation}
  `r DIR_COS_VEC_STD_EQ`.                     (\#eq:direction-cosine-vector-std)
\end{equation}

Operating on Equation \@ref(eq:trait-vector-polar),

\begin{equation}
  \begin{split}
    `r DIR_COS_AS_DIR_COS_STD_EQ` \\
    `r TRAIT_POLAR_COEFF_COS_STD_EQ`
  \end{split}                                 (\#eq:direction-cosine-vectors-eq)
\end{equation}

and, substituting in \@ref(eq:slope-max),

@@

We can define

\begin{equation}
  `r DISCR_VECTOR_STD_EQ`.                               (\#eq:discr-vector-std)
\end{equation}

such that Equation \@ref(eq:slope-max-std-cosines) is similar
(in vectorial form) to Reckase's [-@reckase_difficulty_1985] Equation 6,
and thus can be solved by the same procedure
applying their Equations 7 through 9.
The resulting equivalent to their Equation 9, in vectorial form
and solving for $`r DIR_ANGLE_STD_SUBSTITUTE`$ is

\begin{equation}
  `r DIR_COS_STD_ITEM_VEC_EQ`.                            (\#eq:dir-cos-vec-std)
\end{equation}

Substituting $`r DIR_COS_STD_ITEM_VEC`$ and $`r DISCR_VECTOR_STD`$
by their respective expressions results in the expression for
the direction cosine vector of item $i$ in $`r LATENT_SPACE`$,

@@

which gives the direction from the origin to the point where
the slope is maximum.
Finally, to determine the signed distance $`r DISTANCE_PARAM`$
from the origin to that point,
we solve Equation \@ref(eq:M2PL-formula-polar) for $`r IRF_MAX_SLOPE_EQ`$,
$`r DIR_COS_SUBSTITUTE`$ and
$`r DISTANCE_SUBSTITUTE`$,
and then substitute Equation \@ref(eq:dir-cos-vec) for $`r DIR_COS_ITEM_VEC`$.
The result, solving for $`r DISTANCE_PARAM`$, is

@@

The slope $`r SLOPE_MAX_PARAM`$ at the point defined by Equations
\@ref(eq:dir-cos-vec) and \@ref(eq:distance-param)
is given by Equation \@ref(eq:slope-max).
Solving for $`r DIR_COS_SUBSTITUTE`$
and substituting Equation \@ref(eq:dir-cos-vec) for $`r DIR_COS_ITEM_VEC`$
[@reckase_discriminating_1991],

@@

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
Equation \@ref(eq:slope-param) makes it clear that a space $`r TEST_SPACE`$
with inner product matrix $`r INNER_PROD_MATRIX_INV`$ can be defined,
such that $`r INNER_PROD_DISCR_EQ`$ and, subsequently,
$`r DISCR_VECTOR_MODULE_EQ`$.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of the
discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces,
as their inner product matrices are inverse of one another.

The basis $`r ITEM_SPACE_BASIS_EQ`$ of $`r TEST_SPACE`$ is such that
$`r ITEM_TRANSF_MATRIX_EQ`$ (see Equation \@ref(eq:discr-vector-std)).
Thus, similarly to equation \@ref(eq:dir-cos-vec),
the vector of direction cosines of a vector in $`r TEST_SPACE`$
can be defined as

@@

```{r libraries}
#| message: false
```

```{r sources}
#| message: false
```

@@

```{r set-flextable-wd}
#| cache: false

# Necessary for officedown to find the template file:
opts_knit$set(root.dir = DOC_DIR)
```

```{r example-items-table-out}
#| cache:   false
#| tab_id:  example-items-table-out
#| tab.cap: Item parameters for the graphical example
item_params_output
```

@@

```{r item-plot-out}
#| cache:      false
#| fig.cap:   Item plots in an orthogonal (left) and oblique (right) test space.
#| fig.height: 3.1
#| fig.width:  6.65
plot_orth + plot_oblique
```

@@

```{r read-chunks-empirical-example}
read_chunk("src/Empirical_example.R")
```

@@

```{r set-flextable-wd, cache=FALSE}
```{r set-flextable-wd}
#| cache: false
```

@@

```{r empirical-items-table-out}
#| cache:   false
#| tab.id:  empirical-items-table-out
#| tab.cap: Item parameters for the empirical example
item_params_output
```
